---
title: "Group 31: Task 2- Environmental racism in California - cumulative pollution burden"
author: "Mari Herbst and Abigail Sanford"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach Packages
library(tidyverse)
library(janitor)
library(here)
```

# Read in the Data, then Wrangle it
- Use here() to read in data with a system agnostic file path
- Use janitor::clean_names() to make the columns more coder friendly

```{r}
ces <- read.csv(here("data", "ces3demographics.csv")) %>% # establish file path
  clean_names() # update column names to lower snake case
```

# Data Visualization

```{r}
# create a basic ggplot2 plot showing `white` % on x-axis and CalEnviroScreen pollution burden score on the y-axis. 
ggplot(data = ces, aes(x = white, y = ces_3_0_score)) + 
  geom_hex() + # select graph type
  labs(x = "White Population Percentage", y = "Pollution Burden Score", title = "Pollution Burden Score by White Population Density") +  # add axis titles
  scale_fill_gradient(low = "darkorchid4", high = "darkorchid1") + # add color gradient for density 
  theme_minimal() # change the theme to minimal


```

**Figure 1.** Pollution burden score by white population density: CalEnviroScreen's pollution burden scores shown as a function of percent whiteness of the population in the region. The color scale from dark (low) to light (high) purple indicates the count of regions at a given ratio of pollution burden score to population whiteness.


There is a negative correlation between the pollution burden score and the white population percentage. As pollution burden score increases, percentage of white population decreases.  

**Data Citation**: Office  of  Environmental  Health  and  Hazard  Assessment,  Approaches  for  Identifying  Disadvantaged  Communities  1  (Aug.  2014). Information  available [here](http://oehha.ca.gov/ej/pdf/ApproachesnIdentifyDisadvantagedCommunitiesAug2014.pdf).