---
title: "Untitled"
author: "Mari Herbst and Abigail Sanford"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(janitor)
library(here)
```

- Use here() to read in data with a system agnostic file path
- Use janitor::clean_names() to make the columns more coder friendly

```{r}
ces <- read.csv(here("data", "ces3demographics.csv")) %>% # establish file path
  clean_names() # update column names to lower snake case
```

```{r Abigail}
# create a basic ggplot2 plot showing `white` % on x-axis and CalEnviroScreen pollution burden score on the y-axis. 
ggplot(data = ces, aes(x = white, y = ces_3_0_score)) + 
  geom_hex() + # select graph type
  labs(x = "% white", y = "pollution burden score", title = "Pollution burden score by white population density") +  # add axis titles
  scale_fill_gradient(low = "darkorchid4", high = "darkorchid1") + # add color gradient for density 
  theme_minimal()


```

Figure 1. Pollution burden score by white population density: CalEnviroScreen's pollution burden scores shown as a function of percent whiteness of the population in the region. The color scale from dark (low) to light (high) purple indicates the count of regions at a given ratio of pollution burden score to population whiteness.

